Safe and Robust Formal Synthesis of Digital Controllers\\ for Continuous Plants

### 2018-03-16 automatica/paper.tex
title
section 3

\title{Safe and Robust Formal Synthesis of Digital Controllers for Continuous Plants}
% Title, preferably not more
% than 10 words.

@@

%-------------------------------
\section{Formal specification of control systems properties} 
\label{sec:specification}
%-------------------------------

@@

%-------------------------------
\subsection{Abstract Acceleration of Linear Dynamics} 
\label{ssec:aa}
%-------------------------------

We recall a recently introduced technique called \emph{Abstract Acceleration}~\cite{JSS14,cattaruzza2015unbounded}, 
which will be key in this work for abstraction-based synthesis.  
%\note{This clashes with the model introduced above, with inputs - motivate why? I've added the motivation above by introducing the closed  loop}
Given a model of an iterative program with dynamics
%
\begin{equation}
\vec{x}_{k+1}=\mat{A_d}\vec{x}_k \text{ where } \vec{x}_k \in \mathbb{R}^p, \mat{A_d} \in \mathbb{R}^{p \times p} \text{ and } k \in \mathbb N_0,
\end{equation}
%
\textcolor{red}{[I have modified the notations with the `d' subscript as above.]}
we want to find all possible states visited over an infinite time horizon
starting at an initial set $X_0$.  
This set is known as the \emph{reach tube} of
the model:
%
\begin{equation}
\hat{X} = \{ \vec{x}_k: k \in \mathbb N_0, \vec{x}_0 \in X_0 \text{ and } \vec{x}_{k+1}=\mat{A_d}\vec{x}_k\}.
\end{equation}
%
Using Abstract Acceleration we transform this sequential reachability problem into a one-step problem.  
We first modify the problem statement by means of acceleration into
%
\begin{equation}
\hat{X} = \{ \vec{x}_k=\mat{A_d}^k\vec{x}_0 \mid k \in N_0 \text{ and } \vec{x}_0 \in X_0 \}, 
\end{equation}
%
and further define new model semantics and corresponding set: 
%
\begin{equation}\label{eq:aa_reachtube}
\hat{X} \subseteq \hat{X}^\sharp = \mathcal{A}X_0, \text{ such that } \bigcup_{k \in [0\ \infty)} \mat{A_d}^k \subseteq \mathcal{A}, 
\end{equation}
%
where the newly introduced \emph{abstract reach tube} $\hat{X}^\sharp$ is an
over-approximation of the reach tube of the model \cite{JSS14}.  
In this work we extend the abstract acceleration algorithm to continuous-time models. 
% and  For this reason we must first look at the acceleration of continuous-time dynamics.

@@

The time discretization in Sec.~\ref{sec:model} only allows us to evaluate
the state of the plant at integer multiples of the sample time.  
%\note{Unlike the CAV18 paper, these gain matrices have not been discussed yet. }
However, in order to synthesize $\mat{K}$, 
we must be able to ensure that given properties of the plant hold at any given point in time.  
In order to do so, we accelerate the dynamics of the plant according to the model
semantics in Sec.~\ref{sec:model} and compute the state
$\vec{x}_T$ at a given time $T$,
%
% namely we find an equation for $\tau^n(\vec{x},\vec{u})$ given $\tau(\vec{x},\vec{u})$. 
%
namely the state $\vec{x}(t)$ of the model 
%$\dot{\vec{x}}(t)=\mat{A}
at time $t=T$.

\textcolor{red}{[The following three subsections take too much space, plus the results are mostly known or easily derivable with simple algebra: we need to shorten and simplify it. Dario: can you give it a crack?]}
\textcolor{blue}{[I merged the first two]}

@@

\textcolor{red}{[This paragraph is highly unclear - Dario: can you please update it?]}
\textcolor{blue}{[is  this better?]}

@@

>>>>

\title{Safe and Robust Formal Synthesis of Digital Controllers\\
for Continuous Plants}
% Title, preferably not more
% than 10 words.

@@

%-------------------------------
\section{Formal specification of model properties} 
\label{sec:specification}
%-------------------------------

@@

%-------------------------------
\subsection{Abstract acceleration of linear dynamics} 
\label{ssec:aa}
%-------------------------------

We recall a recently introduced technique called \emph{Abstract Acceleration}~\cite{JSS14,cattaruzza2015unbounded}, 
which will be key in this work for abstraction-based synthesis.  
%\note{This clashes with the model introduced above, with inputs - motivate why? I've added the motivation above by introducing the closed  loop}
Given a model of an iterative program with dynamics
%
\begin{equation}
\vec{x}_{k+1}=\mat{A_d}\vec{x}_k \text{ where } \vec{x}_k \in \mathbb{R}^p, \mat{A_d} \in \mathbb{R}^{p \times p} \text{ and } k \in \mathbb N_0,
\end{equation}
%
we want to find all possible states visited over an infinite time horizon
starting at an initial set $X_0$.  
This set is known as the \emph{reach tube} of the model:
%
\begin{equation}
\hat{X} = \{ \vec{x}_k: k \in \mathbb N_0, \vec{x}_0 \in X_0 \text{ and } \vec{x}_{k+1}=\mat{A_d}\vec{x}_k\}.
\end{equation}
%
Using Abstract Acceleration we transform this sequential reachability problem into a one-step problem. 
This has a lot of benefits ~\cite{JSS14}, not least in terms of numerical error propagation.   
In order to attain this, 
the problem statement is modified, by means of acceleration, into 
%
\begin{equation}
\hat{X} = \{ \vec{x}_k=\mat{A_d}^k\vec{x}_0 \mid k \in N_0 \text{ and } \vec{x}_0 \in X_0 \}, 
\end{equation}
%
and new model semantics and corresponding set are further defined as 
%
\begin{equation}\label{eq:aa_reachtube}
\hat{X} \subseteq \hat{X}^\sharp = \mathcal{A}X_0, \text{ such that } \bigcup_{k \in [0\ \infty)} \mat{A_d}^k \subseteq \mathcal{A}, 
\end{equation}
%
where the newly introduced \emph{abstract reach tube} $\hat{X}^\sharp$ is an
over-approximation of the reach tube of the model \cite{JSS14}.  
\cite{cattaruzza2015unbounded} extends this to LTI models with inputs, 
whereas we next extend the algorithm to continuous-time models, in view of the overall goal of this work. 
% and  For this reason we must first look at the acceleration of continuous-time dynamics.

@@

The time discretization in Sec.~\ref{sec:model} only allows us to evaluate
the state of the plant at integer multiples of the sample time.  
%\note{Unlike the CAV18 paper, these gain matrices have not been discussed yet. }
However, in order to synthesize $\mat{K}$, 
we must be able to ensure that given properties of the plant hold at any given point in time.  
In order to do so, we accelerate the dynamics of the plant according to the continuous-time model
semantics in Sec.~\ref{sec:model}. 
% and compute the state $\vec{x}_T$ at a given time $T$,
%%
%% namely we find an equation for $\tau^n(\vec{x},\vec{u})$ given $\tau(\vec{x},\vec{u})$. 
%%
%namely the state $\vec{x}(t)$ of the model 
%%$\dot{\vec{x}}(t)=\mat{A}
%at time $t=T$.

%\textcolor{red}{[The following three subsections take too much space, plus the results are mostly known or easily derivable with simple algebra: we need to shorten and simplify it. Dario: can you give it a crack?]}
%\textcolor{blue}{[I merged the first two]}

@@

@@

\textcolor{red}{[The next discussion is highly unclear - Dario: can you please update it?]}
